Spectroscopic confirmation of very-wide binaries and large-separation comoving stars from \textsl{Gaia DR1}

### 2017-07-06 paper/comoving-followup.tex
clean up todos, captions

An alternate tracer of the chemical properties mentioned above are
widely-separated ($>XX~\pc$), coeval pairs or multiplets of stars.
These tracers include both bound and unbound wide-separation stellar systems; we
refer to these systems collectively as ``comoving stars'' because, at large
separations with present-day and near-future velocity uncertainties, it is
typically not possible to determine whether these systems are truly bound.
Comoving stars are either wide binaries, disrupted wide binaries, or remnants of
dissolving or disrupted open clusters.
In any of these cases, it is likely that the stars formed from the same region
of a birth cloud, yet are separated enough that there has not been any
cross-pollution in the event of strong stellar winds or stellar evolution.

@@

In this work, we present a catalog of genuine comoving star pairs discovered
through radial velocity follow-up of candidate comoving stars selected from
inferences using their astrometry alone (\citealt{Oh:2017}).
This work serves as a pilot study for data expected in upcoming data releases
from the \gaia\ mission.
We describe the data, observations, and spectroscopic reduction in
\sectionname~\ref{sec:data}.
If you are uninterested in these details, skip to \sectionname~\ref{sec:results}
where we discuss our main results.

@@

In previous work, we have identified a sample of high-confidence, candidate
comoving star pairs (\citealt{Oh:2017}) using only astrometric information from
the \tgas\ catalog (\citealt{Michalik:2015,Gaia-Collaboration:2016a}).
These comoving pairs were selected using a cut on a marginalized likelihood
ratio computed for all nearly co-spatial pairs of stars.
Briefly, likelihood 1, $L_1$, considers a model in which the full-space
velocities of each star in the pair are identical and sampled from a disk-like,
Sun-relative velocity distribution, and likelihood 2, $L_2$, considers a model
in which the full-space velocities of each star were drawn independently from
the same velocity distribution used above; the likelihood ratio is computed as
$L_1/L_2$.
After a parallax signal-to-noise ratio (SNR) cut ($\pi/\sigma_\pi > 8$), we
compute the likelihood ratio for all stars within $10~\pc$ of each target star
from the \tgas\ catalog.
The likelihoods appropriately take into account the reported covariances and
uncertainties between the astrometric measurements in the \tgas\ catalog and
naturally handle geometric or projection effects in comparing spherical
velocity components for star pairs separated by large angles on the sky.
After applying a conservative cut on the likelihood ratio motivated by
computing the same likelihood ratio for random pairings of stars, we find
13,058 comoving star pairs with physical separations between $10^3~\au$ and
$10~\pc$.
Of these pairs, there are 10,606 unique sources, implying that a significant
fraction of the identified pairs are members of larger groups.
$\approx$4,000 of the pairs are mutually exclusive, i.e. neither member is
paired with other stars.
For a full description of the selection method, see \citealt{Oh:2017}.

To select candidate pairs for follow-up spectroscopic observations, we only
consider mutually exclusive star pairs within $200~\pc$ in Heliocentric
distance; with the SNR cut used above and given the limitations of the \tgas\
catalog itself, \tgas\ is $\approx$90\% complete to $200~\pc$
(\citealt{Bovy:2017}).
From this source target list, we randomly observed targets with airmass $\sec z
< 1.5$.
\figurename~\ref{fig:sample-cmd} shows a color-magnitude diagram of all targets
observed in this observing run (markers) plotted over the density of all \tgas\
stars within $200~\pc$.

@@

We observed a total of 765 unique sources over 5 nights from (UT) 2017-03-11 to
2017-03-15, corresponding to 323 unique star pairs and $\approx 120$
calibration targets.
The calibration targets have previously measured radial velocities and chemical
abundances, which will be used for validation of our reduction pipeline and in
future work to measure metallicities and stellar parameters for each observed
source using \project{The Cannon} (\citealt{Ness:TODO}).
The spectra were reduced and calibrated using a custom, publicly-available
pipeline written in \python, described below.

@@

We start the wavelength calibration by interactively identifying the 12
strongest, least blended emission lines in one of the extracted 1D comparison
lamp spectra by comparing to \todo{NIST??}.
Once a rough mapping from pixel to wavelength is determined, we then fit for
the individual line centroids in each comparison lamp spectrum by extracting
small, 8 pixel-wide segments of spectrum around each identified emission line
and fitting a model for the line profile and background to each individually.
We use a pixel-convolved Gaussian profile for each emission line with
parameters: amplitude, $A$; centroid, $x_0$; and root-variance, $\sigma_G$.
We find that nearby blended or low-amplitude lines (i.e. part of the
``background'') sometimes bias the line centroid determination when using a
simple background model.
We therefore model the background flux around each comparison lamp emission
line using a constant offset + Gaussian process (GP).
For the GP model, we use a Mat\'ern 3/2 kernel function
(\citealt{Matern:1986,Rasmussen:2005}) parametrized by amplitude parameter
$\sigma_{3/2}$ and correlation scale $\rho_{3/2}$.
We use \package{celerite} (\citealt{Foreman-Mackey:2017}) to evaluate the full
likelihood for this model, and maximize the (log-)likelihood again using
\lbfgsb\ optimization.
We optimize over the logarithm of any scale parameters (i.e. $A$, $\sigma_G$,
$\sigma_{3/2}$, and $\rho_{3/2}$).
Once we determine the pixel centroids for all identified emission lines for a
given night's comparison lamp spectrum, we then fit an interpolating function
to the pixel-centroid, wavelength values for each emission line.

Typically, high-order standard polynomials or Chebyshev polynomials are used to
fit for the wavelength dispersion function.
We found that using such functions can lead to vastly incorrect wavelength
values near either end of the pixel grid where the polynomial function is
un- or weakly-constrained.
We instead use a combined linear polynomial + GP to model the wavelength
dispersion.
We again use a Mat\'ern 3/2 kernel, use \lbfgsb\ optimization, and convert any
scale parameter to log-space before maximizing the log-likelihood.
\figurename~\ref{fig:wavelength-GP} shows an example of the residuals from one
such fit; black points show the (pixel-centroid, wavelength) pairs with the
best-fit model subtracted.
The envelope around zero (shaded region, orange) shows the \todo{1$\sigma$ blah
blah GP...}
When the GP variance is large, the pixel-to-wavelength mapping is uncertain.
We therefore only use the pixel range from 250--1210, corresponding to a
wavelength range of $\approx 5500$--$7400~{\rm \AA}$; gray shaded region shows
the excluded pixel/wavelength ranges.

This wavelength calibration procedure produces a nightly model for the
nonlinear dispersion of wavelength as a function of pixel value for each
extracted 1D spectrum.
However, because of flexure in the spectrograph, each observation will have an
additional offset of, typically, $\approx 0.5$--$2~{\rm \AA}$, corresponding to
a significant velocity offset at \Ha\ of $\approx 25$--$100~\kms$.
\figurename~\ref{fig:sample-spectra} shows a random sample of 10
wavelength-calibrated source spectra of comoving star pair members normalized
to 1 at $\lambda = 5500~{\rm \AA}$ and shifted by index for visualization.
Suggested by the features in these 10 spectra, there is a mix of metallicities
and spectral types amongst the observed targets.
Note that the spectra are not flux-calibrated, as we only care about measuring
radial velocities from this sample.

@@

As mentioned, comparison lamp spectra were not obtained at each telescope
pointing.
The absolute wavelength solution at each pointing can therefore be shifted
(in pixels) relative to the nightly comparison lamp spectrum because of flexure
in the instrument.
We have found that this offset depends primarily on the hour angle of the
observation, likely because of the physical orientation of the spectrograph and
CCD as mounted on the telescope.
To correct each source spectrum for this offset, we measure the centroids of
the two prominent [OI] sky emission lines near $5577~{\rm \AA}$ and $6300~{\rm
\AA}$ in the corresponding background spectrum derived from the spectral
extraction (described above).
We use a pixel-convolved Voigt profile as the emission line model (same
parameters as above) and a Gaussian process with a Mat\'ern 3/2 kernel function
for the background spectrum (same parameters as above).
We again use \lbfgsb\ optimization and convert any scale parameter to log-space
before maximizing the log-likelihood of this model to derive the line centroid
in wavelength units.
We compute wavelength offsets from true (air) values of the line centroids,
$5577.3387~{\rm \AA}$ and $6300.304~{\rm \AA}$ respectively,\footnote{\url{http:
//physics.nist.gov/PhysRefData/ASD/lines_form.html}} then convert these
wavelength offsets to pixel offsets.
We take the mean of the pixel offsets and apply the derived shift to the source
spectrum before re-computing the wavelength grid using the nightly wavelength
solution \todo{is this sensible?}.
When one or both of the two sky lines is not present or the centroid fit fails,
the spectrum \todo{flagged in some way, can have large absolute velocity
systematic error.}

To derive radial velocities for each source, we then measure the (wavelength)
line centroid of \Ha\ in each corrected spectrum.
We model the absorption line using a pixel-convolved Voigt profile and use a
linear model + a Gaussian process for the background model.
We now use \lbfgsb\ optimization and the resulting maximum-likelihood parameters
to initialize a Markov Chain Monte Carlo (MCMC) sampling of the posterior
probability distribution (PDF) over the 8 parameters: $\ln |A|$, $x_0$,
$\ln\sigma_G$, $\ln\gamma_L$, $\alpha_1$, $\alpha_2$, $\ln\sigma_{3/2}$, and
$\ln\rho_{3/2}$ where the linear background model is defined as $f(\lambda) =
\alpha_1 + \alpha_2\,\lambda$.
The linear amplitude, $A$, is assumed to be negative (i.e. \Ha\ is assumed to be
an absorption feature) and is computed from the corresponding parameter as $A =
-\exp(\ln |A|)$.
We use uniform priors on all parameters except $\ln\rho_{3/2}$, for which we use
a Gaussian; prior parameters are specified in \tablename~\ref{tbl:prior-bounds}.
We use \package{emcee} (\citealt{Foreman-Mackey:2013}) with 64 walkers to
generate samples from the posterior PDF.
We initially run the sampler for 128 steps from the maximum likelihood parameter
values, then resample walker positions in a small ball around the median final
walker positions and run again for 512 steps; together, these two steps
constitute our burn-in phase.
From the final walker positions after burn-in, we run again for 1024 steps and
store these as our posterior samples.
\figurename~\ref{fig:Halpha-mcmc-corner} shows a \package{corner} plot
(\citealt{Foreman-Mackey:2016}) of all projections of these posterior PDF
samples for a randomly-chosen source (HD\todo{XXXX}, in this case).
The marginal posterior distribution over $x_0$ can be converted to a
distribution over radial velocities; in this case, the estimated (Gaussian
standard deviation) precision is $\approx 2.5~\kms$.
\figurename~\ref{fig:Halpha-mcmc-fit} shows the segment of the source spectrum
around \Ha\ used in the line modeling (black line) with uncertainties (grey
bars).
Top panel shows the linear polynomial + absorption line model computed for the
median sample (dark green line); shaded region shows the 15th to 85th
percentiles computed from all posterior samples.
Bottom panel shows the residuals of the data from the median linear polynomial +
absorption line model (black line) along with the Gaussian process computed from
the median parameters (orange curve) used to model other structure in the
vicinity of \Ha (which can be interpreted as correlated noise).
These figures are produced for all source spectrum fits and visually inspected
to ensure that the MCMC sampling appears to have converged for all cases.

For each source spectrum, with the resulting posterior samples, we compute the
median and median absolute deviation (MAD) of the marginal distribution over
line centroid, $x_0$.
We use the MAD to estimate the standard deviation ($\sigma \approx 1.5\times{\rm
MAD}$, assuming the samples are Gaussian distributed) of the samples and find
that the typical velocity \emph{precision} from measuring the centroid of \Ha\
is between $2$--$8~\kms$ \todo{double check numbers}.

@@

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{mcmc_corner.pdf}
  \end{center}
  \caption{%
    \todo{Some summary plots about the MCMC fits...}
    Small uncertainty in centroid = 2 km/s velocity precision here.
    \label{fig:Halpha-mcmc-corner}}
\end{figure}

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{mcmc_example_fit.pdf}
  \end{center}
  \caption{%
    Top shows background linear model + Voigt line model.
    \label{fig:Halpha-mcmc-fit}}
\end{figure}

@@

\figurename~\ref{fig:dx-dv} shows the magnitude of the 3D velocity difference
plotted against the 3D positional separation of the two stars in all observed
pairs.
We again plot the median of the velocity difference distribution, and here use
the Lutz-Kelker-corrected distance estimate (\citealt{Lutz:1973}) computed from
the stars' \tgas\ parallax measurements to compute the 3D positions of the two
stars.
Small, grey markers are pairs for which $\llrnew < \llrold$, i.e. where the
radial velocity measurements weaken or change our belief that a given pair is
comoving.
Larger, black markers are genuine comoving pairs ($\llrnew > \llrold$); note
that many large-separation pairs have been ruled-out as comoving, but
most small-separation pairs maintain their status as comoving.
This is also apparent in \figurename~\ref{fig:separation}, which shows
histograms of the spatial separation and sky separation for all pairs;
background, grey histogram shows all observed pairs, and foreground, black
histogram shows all pairs for which $\llrnew > \llrold$.

@@

\section{Discussion}

>>>>

An alternate tracer of the chemical properties mentioned above are
widely-separated ($\gtrsim 0.01~\pc$), coeval pairs or multiplets of stars.
These tracers include both bound and unbound wide-separation stellar systems; we
refer to these systems collectively as ``comoving stars'' because, at large
separations with present-day and near-future velocity uncertainties, it is
typically not possible to determine whether these systems are truly bound.
Comoving stars are either wide binaries, disrupted wide binaries, or remnants of
dissolving or disrupted open clusters.
In any of these cases, it is likely that the stars formed from the same region
of a birth cloud, yet are separated enough that there has not been any
cross-pollution in the event of strong stellar winds or stellar evolution.

@@

In this work, we present a catalog of genuine comoving star pairs discovered
through radial velocity follow-up of candidate comoving stars selected from
inferences using their astrometry alone (\citealt{Oh:2017}).
This work serves as a pilot study for data expected in upcoming data releases
from the \gaia\ mission.
We describe the data, observations, and spectroscopic reduction in
\sectionname~\ref{sec:data}.
If you are uninterested in these details, skip to \sectionname~\ref{sec:results}
and \sectionname~\ref{sec:discussion} where we present and discuss our main
results.

@@

In previous work, we have identified a sample of high-confidence, candidate
comoving star pairs (\citealt{Oh:2017}) using only astrometric information from
the \tgas\ catalog (\citealt{Michalik:2015,Gaia-Collaboration:2016a}).
These comoving pairs were selected using a cut on a marginalized likelihood
ratio computed for all nearly co-spatial pairs of stars.
Briefly, likelihood 1, $L_1$, considers a model in which the full-space
velocities of each star in the pair are identical and sampled from a disk-like,
Sun-relative velocity distribution, and likelihood 2, $L_2$, considers a model
in which the full-space velocities of each star were drawn independently from
the same velocity distribution used above. The computed likelihood ratio is
actually the the ratio of fully marginalized likelihoods,
$\mathcal{L}_1/\mathcal{L}_2$, after marginalizing over true velocity and
distance for each star in a given pair.
After a parallax signal-to-noise ratio (SNR) cut ($\pi/\sigma_\pi > 8$), we
compute the likelihood ratio for all stars within $10~\pc$ of each target star
from the \tgas\ catalog.
The likelihoods appropriately take into account the reported covariances and
uncertainties between the astrometric measurements in the \tgas\ catalog and
naturally handle geometric or projection effects in comparing spherical
velocity components for star pairs separated by large angles on the sky.
After applying a conservative cut on the likelihood ratio motivated by computing
the same likelihood ratio for random pairings of stars ($\ln
\mathcal{L}_1/\mathcal{L}_2 > 6$, we find 13,058 comoving star pairs with
physical separations between $10^3~\au$ and $10~\pc$.
Of these pairs, there are 10,606 unique sources, implying that a significant
fraction of the identified pairs are members of larger groups.
$\approx$4,000 of the pairs are mutually exclusive, i.e. neither member is
paired with other stars.
For a full description of the selection method, see \citealt{Oh:2017}.

To select candidate pairs for follow-up spectroscopic observations, we only
consider mutually exclusive star pairs within $200~\pc$ in Heliocentric
distance; with the SNR cut used above and given the limitations of the \tgas\
catalog itself, \tgas\ is $\approx$90\% complete to $200~\pc$
(\citealt{Bovy:2017}).
From this source target list, we randomly observed targets with airmass $\sec z
< 1.5$.
\figurename~\ref{fig:sample-cmd} shows a color-magnitude diagram of all targets
observed in this observing run (markers) plotted over the density of all \tgas\
stars within $200~\pc$.
Candidate comoving pairs are connected by (colored) lines.

@@

We observed a total of 765 unique sources over 5 nights from (UT) 2017-03-11 to
2017-03-15, corresponding to 323 unique star pairs and $\approx 120$
calibration targets.
The calibration targets have previously measured radial velocities and chemical
abundances, which will be used for validation of our reduction pipeline and in
future work to measure metallicities and stellar parameters for each observed
source using \project{The Cannon} (\citealt{Ness:2015}).
The spectra were reduced and calibrated using a custom, publicly-available
pipeline written in \python, described below.

@@

We start the wavelength calibration by interactively identifying the 12
strongest, least blended emission lines in one of the extracted 1D comparison
lamp spectra by comparing to standard HgNe line lists.\footnote{\url{http:
//physics.nist.gov/PhysRefData/ASD/lines_form.html}}
Once a rough mapping from pixel to wavelength is determined, we then fit for the
individual line centroids in each comparison lamp spectrum by extracting small,
8 pixel-wide segments of the comparison lamp spectrum around each identified
emission line and fitting a model for the line profile and background to each
individually.
We use a pixel-convolved Gaussian profile for each emission line with
parameters: amplitude, $A$; centroid, $x_0$; and root-variance, $\sigma_G$.
We find that nearby blended or low-amplitude lines (i.e. part of the
``background'') sometimes bias the line centroid determination when using a
simple background model.
We therefore model the background flux around each comparison lamp emission
line using a constant offset + Gaussian process (GP).
For the GP model, we use a Mat\'ern 3/2 kernel function
(\citealt{Matern:1986,Rasmussen:2005}) parametrized by amplitude parameter
$\sigma_{3/2}$ and correlation scale $\rho_{3/2}$.
We use \package{celerite} (\citealt{Foreman-Mackey:2017}) to evaluate the full
likelihood for this model, and maximize the (log-)likelihood again using
\lbfgsb\ optimization.
We optimize over the logarithm of any scale parameters (i.e. $A$, $\sigma_G$,
$\sigma_{3/2}$, and $\rho_{3/2}$).
Once we determine the pixel centroids for all identified emission lines for a
given night's comparison lamp spectrum, we then fit an interpolating function
to the pixel-centroid, wavelength values for each emission line.

Typically, high-order standard polynomials or Chebyshev polynomials are used to
fit for the wavelength dispersion function.
We found that using such functions can lead to vastly incorrect wavelength
values near either end of the pixel grid where the polynomial function is
un- or weakly-constrained.
We instead use a combined linear polynomial + GP to model the wavelength
dispersion.
We again use a Mat\'ern 3/2 kernel, use \lbfgsb\ optimization, and convert any
scale parameter to log-space before maximizing the log-likelihood.
\figurename~\ref{fig:wavelength-GP} shows an example of the residuals from one
such fit; black points show the (pixel-centroid, wavelength) pairs with the
best-fit model subtracted.
The envelope around zero (shaded region, orange) shows the variance of the GP
model projected into the data space; when the GP variance is large, the
pixel-to-wavelength mapping is uncertain.
We therefore only use the pixel range from 250--1210, corresponding to a
wavelength range of $\approx 5500$--$7400~{\rm \AA}$; gray shaded region shows
the excluded pixel/wavelength ranges.

This wavelength calibration procedure produces a nightly model for the
nonlinear dispersion of wavelength as a function of pixel value for each
extracted 1D spectrum.
However, because of flexure in the spectrograph, each observation will have an
additional offset of, typically, $\approx 0.5$--$2~{\rm \AA}$, corresponding to
a significant velocity offset at \Ha\ of $\approx 25$--$100~\kms$ (discussed
below).
\figurename~\ref{fig:sample-spectra} shows a random sample of 10
wavelength-calibrated source spectra of comoving star pair members normalized
to 1 at $\lambda = 5500~{\rm \AA}$ and shifted by index for visualization.
As suggested by the features in these 10 spectra, there is a mix of
metallicities and spectral types amongst the observed targets.
Note that the spectra are not flux-calibrated, as we only care about measuring
radial velocities from this sample.

@@

As mentioned, comparison lamp spectra were not obtained at each telescope
pointing.
The absolute wavelength solution at each pointing can therefore be shifted
(in pixels) relative to the nightly comparison lamp spectrum because of flexure
in the instrument.
We have found that this offset depends primarily on the hour angle of the
observation, likely because of the physical orientation of the spectrograph and
CCD as mounted on the telescope.
To correct each source spectrum for this offset, we measure the centroids of
the two prominent [OI] sky emission lines near $5577~{\rm \AA}$ and $6300~{\rm
\AA}$ in the corresponding background spectrum derived from the spectral
extraction (described above).
We use a pixel-convolved Voigt profile as the emission line model (same
parameters as above) and a Gaussian process with a Mat\'ern 3/2 kernel function
for the background spectrum (same parameters as above).
We again use \lbfgsb\ optimization and convert any scale parameter to log-space
before maximizing the log-likelihood of this model to derive the line centroid
in wavelength units.
We compute wavelength offsets from true (air) values of the line centroids,
$5577.3387~{\rm \AA}$ and $6300.304~{\rm \AA}$ respectively,\footnote{\url{http:
//physics.nist.gov/PhysRefData/ASD/lines_form.html}} then convert these
wavelength offsets to pixel offsets.
We take the mean of the pixel offsets and apply the derived shift to the source
spectrum before re-computing the wavelength grid using the nightly wavelength
solution.
When one or both of the two sky lines is not present or the centroid fit fails,
the spectrum is flagged as having a suspect wavelength calibration.
In practice, most such sources are calibration targets, which are more likely to
have very short exposure times and thus weak night-sky lines.

To derive radial velocities for each source, we then measure the (wavelength)
line centroid of \Ha\ in each corrected spectrum.
We model the absorption line using a pixel-convolved Voigt profile and use a
linear model + a Gaussian process for the background model.
We now use \lbfgsb\ optimization and the resulting maximum-likelihood parameters
to initialize a Markov Chain Monte Carlo (MCMC) sampling of the posterior
probability distribution (PDF) over the 8 parameters: $\ln |A|$, $x_0$,
$\ln\sigma_G$, $\ln\gamma_L$, $\alpha_1$, $\alpha_2$, $\ln\sigma_{3/2}$, and
$\ln\rho_{3/2}$ where the linear background model is defined as $f(\lambda) =
\alpha_1 + \alpha_2\,\lambda$.
The linear amplitude, $A$, is assumed to be negative (i.e. \Ha\ is assumed to be
an absorption feature) and is computed from the corresponding parameter as $A =
-\exp(\ln |A|)$.
We use uniform priors on all parameters except $\ln\rho_{3/2}$, for which we use
a Gaussian; prior parameters are specified in \tablename~\ref{tbl:prior-bounds}.
We use \package{emcee} (\citealt{Foreman-Mackey:2013}) with 64 walkers to
generate samples from the posterior PDF.
We initially run the sampler for 128 steps from the maximum likelihood parameter
values, then resample walker positions in a small ball around the median final
walker positions and run again for 512 steps; together, these two steps
constitute our burn-in phase.
From the final walker positions after burn-in, we run again for 1024 steps and
store these as our posterior samples.
\figurename~\ref{fig:Halpha-mcmc-corner} shows a \package{corner} plot
(\citealt{Foreman-Mackey:2016}) of all projections of these posterior PDF
samples for a randomly-chosen source (HD 63408, in this case).
The marginal posterior distribution over $x_0$ can be converted to a
distribution over radial velocity; in this case, the estimated (Gaussian
standard deviation) precision is $\approx 2.5~\kms$.
\figurename~\ref{fig:Halpha-mcmc-fit} shows the segment of the source spectrum
around \Ha\ used in the line modeling (black line) with uncertainties (gray
bars).
Top panel shows the linear polynomial + absorption line model computed for the
median sample (dark green line); shaded region shows the 15th to 85th
percentiles computed from all posterior samples.
Bottom panel shows the residuals of the data from the median linear polynomial +
absorption line model (black line) along with the Gaussian process computed from
the median parameters (orange curve) used to model other correlated structure in
the vicinity of \Ha (which can be interpreted as correlated noise).
These figures are produced for all source spectrum fits and visually inspected
to ensure that the MCMC sampling appears to have converged for all cases.

For each source spectrum, with the resulting posterior samples, we compute the
median and median absolute deviation (MAD) of the marginal distribution over
line centroid, $x_0$.
We use the MAD to estimate the standard deviation ($\sigma \approx 1.5\times{\rm
MAD}$, assuming the samples are Gaussian distributed) of the samples and find
that the typical velocity \emph{precision} from measuring the centroid of \Ha\
is between $5$--$10~\kms$.

@@

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{mcmc_corner.pdf}
  \end{center}
  \caption{%
    A corner plot showing all projections of posterior PDF samples for the \Ha\
    line model and the spectrum of the source HD 63408.
    Note the small uncertainty in the line centroid measurement, $x_0$, which
    corresponds to a $\approx 2~\kms$ velocity precision for this source.
    Parameters are described in \sectionname~\ref{sec:reduction}, and prior PDFs
    over the parameters are described in \tablename~\ref{tbl:prior-bounds}.
    \label{fig:Halpha-mcmc-corner}}
\end{figure}

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{mcmc_example_fit.pdf}
  \end{center}
  \caption{%
    Visualization of the \Ha\ absorption line model and fits for the source HD
    63408 as a demonstration of the procedure used for all targets.
    \emph{Top}:
    The source spectrum in a small wavelength range around \Ha\ (black),
    uncertainty in spectral flux (gray error bars).
    Over-plotted is the line model + background computed from the median
    posterior PDF sample (dark green line) and the 15th to 85th percentile
    region computed from all posterior PDF samples (shaded green region).
    \emph{Bottom}:
    Source spectrum residuals computed by subtracting the median model (dark
    green line in top panel) from the source spectrum.
    The over-plotted line (orange) shows the Gaussian process background model
    computed from the median posterior PDF sample.
    \label{fig:Halpha-mcmc-fit}}
\end{figure}

@@

\figurename~\ref{fig:dx-dv} shows the magnitude of the 3D velocity difference
plotted against the 3D positional separation of the two stars in all observed
pairs.
We again plot the median of the velocity difference distribution, and here use
the Lutz-Kelker-corrected distance estimate (\citealt{Lutz:1973}) computed from
the stars' \tgas\ parallax measurements to compute the 3D positions of the two
stars.
Small, gray markers are pairs for which $\llrnew < \llrold$, i.e. where the
radial velocity measurements weaken or change our belief that a given pair is
comoving.
Larger, black markers are genuine comoving pairs ($\llrnew > \llrold$); note
that many large-separation pairs have been ruled-out as comoving, but
most small-separation pairs maintain their status as comoving.
This is also apparent in \figurename~\ref{fig:separation}, which shows
histograms of the spatial separation and sky separation for all pairs;
background, gray histogram shows all observed pairs, and foreground, black
histogram shows all pairs for which $\llrnew > \llrold$.

@@

\section{Discussion} \label{sec:discussion}
